%-------------------------
% Resume in Latex
% Author : Emilio
% Based off of: https://github.com/emilioriosvz/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Emilio Rios} \\ \vspace{1pt}
    \href{mailto:emilioriosvz@gmail.com}{\underline{emilioriosvz@gmail.com}} $|$
    \href{https://linkedin.com/in/emrios}{\underline{linkedin.com/in/emrios}} $|$
    \href{https://github.com/emilioriosvz}{\underline{github.com/emilioriosvz}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Chief Technology Officer}{Jun 2023 -- Present}
      {Storimake}{Madrid, Spain (Remote)}
      \resumeItemListStart
        \resumeItem{Restructured the team, enhancing remote work and cross-department collaboration, while leading software and product development to deliver fast, affordable services with a seamless user experience.}
        \resumeItem{Led the migration from a mobile app to a web-based platform based on market research, redesigning services to ensure scalability and performance, reducing response times by up to 40\% and cutting feature delivery times from months to days.}
        \resumeItem{Implemented a continuous deployment pipeline, moving from 2 monthly releases to up to 10 production deploys per week (+1900\%), significantly enhancing product agility and responsiveness to user feedback.}
      \resumeItemListEnd

    \resumeSubheading
      {Principal Backend Engineer}{Feb 2024 -- Jan 2025}
      {Dott}{Chicago, US (Remote)}
      \resumeItemListStart
        \resumeItem{Led the design and implementation of scalable backend systems, ensuring reliability and performance to support growth and user acquisition in the US market}
        \resumeItem{Optimized backend architecture and performance, driving key decisions on system design and feature enhancements to scalability.}
        \resumeItem{Developed and led the research and development of innovative video tools, enabling users and companies to seamlessly convert their pictures into cinematic stories through automated workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Founder}{Barcelona, Spain (Remote)}
      {The Crafters Lab}{Jan 2021 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Spearheaded the overall business strategy, driving digital transformation for businesses through innovative, end-to-end solutions.}
        \resumeItem{Drove the company’s growth by securing new clients and maintaining strong relationships with existing ones, which led to collaborations with major clients such as Wefox, FlaixFM, and other leading agencies in Spain.}
        \resumeItem{Managed both business and technical operations, aligning technology with client goals, which helped generate over €200k in cash flow during the first year with a very small team.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Software Engineer}{Mar 2020 -- Dec 2021}
      {Wefox}{Berlin, Germany (Remote)}
      \resumeItemListStart
        \resumeItem{Developed an API that reduced the time-to-market for new insurance products from months to weeks, accelerating product launches and improving operational efficiency.}
        \resumeItem{Designed a strategy to transition from a monolithic architecture to modular components using Domain-Driven Design (DDD), improving scalability and reliability while enabling future microservices.}
        \resumeItem{Designed and implemented a testing strategy that increased test coverage by over 95\%, significantly reducing bugs in production and improving overall system stability.}
        \resumeItem{Implemented a new CI/CD pipeline with the team, drastically reducing deployment times and increasing the number of weekly deployments.}
        \resumeItem{Led the rollout of a new development methodology, presenting its importance to over 100 technical staff, resulting in up to a 10x improvement in efficiency across the organization.}
      \resumeItemListEnd

    \resumeSubheading
      {Engineering Lead}{Apr 2018 -- Mar 2020}
      {Apartum.com}{Barcelona, Spain}
      \resumeItemListStart
        \resumeItem{Led the backend team, optimizing apartment comparison systems across millions of listings.}
      \resumeItemListEnd

    \resumeSubheading
      {Staff augmenting positions}{2015 -- 2018}
      {Various companies}{Spain}
      \resumeItemListStart
        \resumeItem{Mobdala -   Barcelona, Spain}
        \resumeItem{Cl3ver -    Barcelona, Spain}
        \resumeItem{Huballin -  Barcelona, Spain}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Fauna Valley}  $|$ \emph{Ruby on Rails, Nodejs, React, Postgres}}{Apr 2014 -- Dec 2016}
          \resumeItemListStart
            \resumeItem{Awarded Best Project of the Year at La Salle Gracia for creating a platform aimed at preventing exotic animal trafficking.}
            \resumeItem{Developed a system enabling legal owners of exotic animals to share them for breeding, preserving genetic diversity and reducing the need for wild captures.}
            \resumeItem{Implemented a frontend to educate users on optimal conditions for exotic species care, raise awareness about the environmental impact of illegal exotic pet trade, and promote sustainable breeding practices.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://cursoby.com}{\underline{Cursoby}}}  $|$ \emph{Nodejs, Nextjs, Typescript, MongoDB}}{Feb 2023 -- Nov 2023}
          \resumeItemListStart
            \resumeItem{Developed a scraping tool to collect data from various sources and store it in a database}
            \resumeItem{Designed and implemented a RESTful API to serve the data to the frontend}
            \resumeItem{Built a frontend application using Nextjs and Typescript to display the data to users}
            \resumeItem{Optimized the application for SEO and performance to increase organic traffic}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://dondever.com}{\underline{Dondever}}}  $|$ \emph{Nodejs, Nextjs, Typescript, MongoDB}}{Apr 2023 -- Dec 2023}
          \resumeItemListStart
            \resumeItem{Designed and implemented a RESTful API to manage films information}
            \resumeItem{Ingested data through scrapers and integrated third-party APIs to fetch additional information such as ratings, reviews, and posters.}
            \resumeItem{Built a frontend application focused on SEO to increase organic traffic}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Typescript, SQL} \\
     \textbf{Frameworks and Libraries}{: Node.js, Electron, Next.js, Tailwind CSS} \\
     \textbf{Data management}{: PostgreSQL, MySQL, MongoDB, Redis} \\
     \textbf{Developer Tools}{: Git, VSCode, iTerm, Docker} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
